Ode to Reviewer Two

### 2016-03-07 ode/ode.tex
fix ode punctuation

\noindent
My paper submitted, the deadline complete;\\
The product of months of lonely toil,\\
With quality prose and experiments replete\\
Amid insecurities, fears, and other turmoil.\\
Though once I feared a harsh rejection,\\
My advisor assured me that my proofs were sound\\
And my treatment of the work related, fair,\\
So I've come to believe in the paper's perfection.\\
Through this research, new self-confidence found,\\
Though all-nighters have left me exhausted and drowned.\\
Now waiting for judgement from reviewers elsewhere.\\
\\
But alas! Though first and third reviewers were happy,\\
Reviewer the second couldn't seem to accept.\\
He gave reasons he thought my paper was crappy,\\
But I found his attempted critique most inept.\\
His comments betrayed a misunderstanding\\
And nonsense ``suggestions'' were falsely polite,\\
Completely missing the point of my work,\\
I couldn't believe what he was demanding:\\
To re-run experiments, perhaps out of spite;\\
An unrelated paper he asked me to cite!\\
(Probably his own.) What a jerk.\\
\\
With a glimmer of hope, I wrote a rebuttal\\
Appealing to reviewers One and Three impressed,\\
And suggested to Two, hey, you missed something subtle?\\
You'll reconsider, I desp'rately expressed.\\
The final suggestions were naught but derision:\\
``Clearly elaborate!'' was all Two replied,\\
Hiding the true message that he was outwit;\\
But it was too late to change their decision.\\
My paper rejected, my joy and pride,\\
My confidence collapsed in a sudden landslide;\\
Now to find somewhere to resubmit.\\

>>>>

\noindent
My paper submitted, the deadline complete;\\
The product of months of lonely toil,\\
With quality prose and experiments replete\\
Amid insecurities, fears, and other turmoil.\\
Though once I feared a harsh rejection,\\
My advisor assured me that my proofs were sound\\
And my treatment of the work related, fair,\\
So I've come to believe in the paper's perfection.\\
Through this research, new self-confidence found,\\
Though all-nighters have left me exhausted and drowned.\\
Now waiting for judgement from reviewers elsewhere.\\
\\
But alas! Though first and third reviewers were happy,\\
Reviewer the second couldn't seem to accept.\\
He gave reasons he thought my paper was crappy,\\
But I found his attempted critique most inept.\\
His comments betrayed a misunderstanding\\
And nonsense ``suggestions'' were falsely polite,\\
Completely missing the point of my work.\\
I couldn't believe what he was demanding:\\
To re-run experiments, perhaps out of spite;\\
An unrelated paper he asked me to cite!\\
(Probably his own.) What a jerk.\\
\\
With a glimmer of hope, I wrote a rebuttal\\
Appealing to reviewers One and Three impressed,\\
And suggested to Two, hey, you missed something subtle?\\
You'll reconsider, I desp'rately expressed.\\
The final suggestions were naught but derision:\\
``Clearly elaborate!'' was all Two replied,\\
Hiding the true message that he was outwit;\\
But it was too late to change their decision.\\
My paper rejected, my joy and pride,\\
My confidence collapsed in a sudden landslide;\\
Now to find somewhere to resubmit.\\
